The problem and promise of scale in multilayer networks

### 2020-01-22 paper/manuscript.Rmd
update ms

---
title: The problem and promise of scale in multilayer networks
author: Alec L. Robitaille, Quinn M.R. Webber, Julie W. Turner, Eric Vander Wal
output: github_document
---

@@

Continuous collection of animal relocation data using GPS technology can be used to measure how groups of animals make movement decisions in the context of their local environment (Strandburg-Peshkin et al. 2015, 2017) and across scales. A collective movement layer could constitute similarity in movement for dyads (Long et al. 2014) or groups (Bode et al. 2011) as well as at a fine (i.e. minute-to-minute: Cleasby et al. 2019) or coarse (global migration: Flack et al. 2018) scales. Importantly, the key to incorporating movement in multilayer networks across scales is the technological advancements available to overcome previous limitations (see Hughey et al. 2018).

>>>>

---
title: The problem and promise of scale in multilayer networks
author: Alec L. Robitaille, Quinn M.R. Webber, Julie W. Turner, Eric Vander Wal
output: 
    word_document
    #github_document
---

@@

Continuous collection of animal relocation data using GPS technology can be used to measure how groups of animals make movement decisions in the context of their local environment (Strandburg-Peshkin et al. 2015, 2017) and across scales. A collective movement layer could constitute similarity in movement for dyads (Long et al. 2014) or groups (Bode et al. 2011) as well as at a fine (i.e. minute-to-minute: Cleasby et al. 2019) or coarse (global migration: Flack et al. 2018) scales. Another potential application would be to generate social networks during times when animals are engaged in different behaviours, including moving, interacting, or foraging (e.g. Muller et al. 2018; Finn et al. 2019) and construct a multilayer networks based on behaviour-specific monolayer networks (e.g. Smith-Aguilar et al. 2019) In contrast to spatial networks, movement networks could assimilate dyadic movement metrics into a network representing the continuous and simultaneous movement trajectories of animals. Importantly, the key to incorporating movement in multilayer networks across scales is the technological advancements available to overcome previous limitations (see Hughey et al. 2018).

Given the existing framework for constructing multilayer networks from behavioural layers (e.g. Smith-Aguilar et al. 2019), movement layers could be integrated with interaction or association layers. Integrating movement layers with habitat-specific social association layers could further shed light on the role of movement as a driver of the social and spatial environments an individual experiences (Webber and Vander Wal 2018). In our case study, we generated multilayer networks based on habitat-specific monolayers. Coordinated movement of dyads, or groups, could vary based on habitat and the approach we outline could be used to explore mechanisms linking the social and spatial environments. For example, social processes may be an emergent property of the landscape because animals aggregate at resources, such as waterholes (Chamaillé-Jammes et al. 2008), while movement to, from, or within habitat patches can also contribute to the formation of the social environment (Spiegel et al. 2016). Incorporating movement ecology within a multilayer network framework is a logical next step for a burgeoning field. In particular, when association networks are habitat-specific, we suggest the integration of movement and space use in multilayer networks provides novel insight into the
